---
title: "reesehs_OriginalHomeworkCode_05"
author: "Reese Hotten-Somers"
date: "2023-11-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1: Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).

```{r, prelims}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall23/KamilarAndCooperData.csv") #imports data from Kamilar/Cooper data
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)  #reads data and creates data frame from it
head(d) #returns data frame

```

```{r, q1}
ml <- lm(data = d, log(HomeRange_km2)~log(Body_mass_female_mean)) #fits linear model to data
summary(ml)

ml$coefficients #states beta coefficients 

ci <- confint(ml, level = 0.95) #get confidence interval
ci

```

## Question 2: Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β
 coefficient. 
```{r, q2}
set.seed(123)
library(boot)

bstat <- function(formula, data, indices){
  d <- data[indices,] #allows bootstrap 
  fit <- lm(formula, data = d)
  return(fit$coefficients)
} #creates function for the boot function

results <- boot(d, statistic = bstat, R=1000, formula = log(HomeRange_km2)~log(Body_mass_female_mean))#bootstraps the data 1000 times and takes the lm each time
print(results)


boot.ci(results, type = "bca", index = 1) #CI for intercept
boot.ci(results, type = "bca", index = 2) #CI for slope

#this website was incredibly helpful!: https://www.r-bloggers.com/2022/12/how-to-perform-bootstrapping-in-r/#google_vignette
```


## Discussion: 
How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
  The SE for the lm() betas/coefficients were 0.67293 and 0.08488. While the SEs for the bootstrap were 0.59240029 0.07677337. Bootstrapping allowed for slightly lower SE values. 
  
How does the latter compare to the 95% CI estimated from your entire dataset?
  The CI lm() intercept was -10.7720889, -8.110374 and for slope 0.8685707  1.204292. Whereas the bootstrap CI for intercept was -10.597,  -8.278 and slope 0.886,  1.187. Bootstraping caused small diferences in the CI leading to a lower range but not by much. 

## Challenges 
Honestly I didn't really struggle with this weeks homework. The website I found was incredbily helpful in understanding the boot() function. 

## Peer Commentary (Jess)
Great job with this homework assignment, Reese! Our codes for both questions are nearly identical. I'm grasping at straws because your work is already outstanding but here are a few minor adjustments that could be made:

- In Question #2, there is an additional space between the terms β and coefficient. 
- Embed your website links instead of just adding the URL; it gives the Rmd file a cleaner look. To do this: [website] (URL Link)
- Consider adding an Rmd theme; they make things so FUN.
- In the discussion section (paragraph #2), the word "bootstrapping" is misspelled.
- In the challenges section, the word "incredibly" is misspelled. 